R Notebook

### 2023-11-20 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
fitbiiiiit

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2,
      apaTables,
      rockchalk)

@@

## Interview phase

```{r}
main %>% 
  filter(time_span == "interview") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            # gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         # gender = if_else(gender == "male",
         #                   true = 0,
         #                   false = 1),
         teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) -> cor_interview

@@

summary(regr_preparation1)
summary(regr_preparation2)
summary(regr_preparation3)
summary(regr_preparation4)

@@

# Multiple Linear Regression (Slope)
```{r}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") 
  # %>% 
  # mutate(slope = abs(slope))
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

@@

  cache <- df-multi %>% 
    filter(time_span == i)

@@

summary(regr_preparation1)
summary(regr_preparation2)
summary(regr_preparation3)
summary(regr_preparation4)

@@

# Pre Teaching Phase

```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") 
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

fit_pre_1 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience + disruption)

@@

getDeltaRsquare(fit_pre_1)

dat1 <- genCorrelatedData(N=250, means=c(100,100),
sds=c(30,20), rho=0.0,  stde = 7, beta=c(1.1, 2.4, 4.1, 0))
m1 <- lm(y ~ x1 + x2, data=dat1)
getDeltaRsquare(m1)

# fit_pre_2 <-
#   df_multi %>% 
#   filter(Phase == "Pre Teaching Phase") %$% 
#   lm(slope ~ confidence)
# 
# summary(fit_pre_2)
# 
# 
# fit_pre_3 <-
#   df_multi %>% 
#   mutate(teaching_experience = log(teaching_experience + 1)) %>% 
#   filter(Phase == "Pre Teaching Phase") %$% 
#   lm(slope ~ teaching_experience)
# 
# summary(fit_pre_3)
# 
# 
# fit_pre_4 <-
#   df_multi %>% 
#   filter(Phase == "Pre Teaching Phase") %$% 
#   lm(slope ~ confidence + disruption)
# 
# summary(fit_pre_4)
# 
# fit_pre_5 <-
#   df_multi %>% 
#   filter(Phase == "Pre Teaching Phase") %$% 
#   lm(slope ~ confidence + disruption + teaching_experience)
# 
# summary(fit_pre_5)
# 
# 
# stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
#                      type = "html",
#                      caption = "Pre Teaching Phase",
#                      dep.var.labels = "Slope",
#                      # order = c(1, 2, 3),
#                      # covariate.labels = c("Disruption Factor",
#                      #                      "Confidence Factor",
#                      #                      "Teaching Experience"),
#                      keep.stat = c("n","rsq","adj.rsq")
#                      )

# fit_pre_3$model %>%
#   mutate(fitted.values = fit_pre_3$fitted.values) %>% 
#   ggplot(mapping = aes(x = teaching_experience,
#                        y = slope
#                        )
#          ) +
#   geom_point(mapping = aes(group = posneg)) +
#           geom_line(mapping = aes(y = fitted.values,
#                                   group = posneg)) +
#   geom_smooth(method = "lm",
#               se = F,
#               linetype = "dashed") +
#         # geom_point(alpha = 0.5,
#         #            size = 0.5) +
#         theme_apa()

>>>>

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2,
      apaTables)

@@

## Interview phase
```{r}
main %>% 
  filter(time_span == "interview") %>% 
  group_by(ID) %>% 
  transmute(heart_rate_m = mean(heart_rate_std),
            confidence_factor_m = mean(confidence_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            teaching_experience = teaching_experience,
            # gender = gender
  ) %>%
  distinct() %>% 
  ungroup() %>% 
  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
         # gender = if_else(gender == "male",
         #                   true = 0,
         #                   false = 1),
         teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
         ) -> cor_interview

@@

summary(regr_end1)
summary(regr_end2)
summary(regr_end3)
summary(regr_end4)

# delta R²
summary(regr_end1)$r.squared - summary(regr_end2)$r.squared - summary(regr_end3)$r.squared - summary(regr_end4)$r.squared

@@

# Multiple Linear Regression (Slope)
```{r}
df_multi <- 
  main %>% 
  select("ID",
         "disruption_factor",
         "confidence_factor",
         "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID),
         ) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>%
  mutate(time_span = factor(Phase,
                             levels = c("Pre Teaching Phase",
                                        "Teaching Phase",
                                        "Post Teaching Phase",
                                        "Interview Phase",
                                        "End Phase"),
                             labels = c("preparation",
                                        "teaching",
                                        "post",
                                        "interview",
                                        "end")
                            )
         ) %>%
  select("id",
         "disruption_factor",
         "confidence_factor",
         "teaching_experience",
         "slope",
         "time_span")

  # %>% 
  # mutate(slope = abs(slope))
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

@@

  cache <- df_multi %>% 
    filter(time_span == i)

  regr1 <-
    lm(slope ~ teaching_experience,
    data = cache)

@@

summary(regr_post1)
summary(regr_post2)
summary(regr_post3)
summary(regr_post4)

summary(regr_end1)$r.squared - summary(regr_end2)$r.squared - summary(regr_end3)$r.squared - summary(regr_end4)$r.squared

@@

# Pre Teaching Phase
```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id")
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

fit_pre_1 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience)

@@

fit_pre_2 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience + disruption_factor)

summary(fit_pre_2)

summary(fit_pre_1)$r.squared - summary(fit_pre_2)$r.squared

fit_pre_3 <-
  df_multi %>% 
  mutate(teaching_experience = log(teaching_experience + 1)) %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience + confidence_factor)

summary(fit_pre_3)

summary(fit_pre_1)$r.squared - summary(fit_pre_2)$r.squared - summary(fit_pre_3)$r.squared

fit_pre_4 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience + confidence + disruption)

summary(fit_pre_4)

stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
                     type = "html",
                     caption = "Pre Teaching Phase",
                     dep.var.labels = "Slope",
                     # order = c(1, 2, 3),
                     # covariate.labels = c("Disruption Factor",
                     #                      "Confidence Factor",
                     #                      "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )

fit_pre_3$model %>%
  mutate(fitted.values = fit_pre_3$fitted.values) %>% 
  ggplot(mapping = aes(x = teaching_experience,
                       y = slope
                       )
         ) +
  geom_point(mapping = aes(group = posneg)) +
          geom_line(mapping = aes(y = fitted.values,
                                  group = posneg)) +
  geom_smooth(method = "lm",
              se = F,
              linetype = "dashed") +
        # geom_point(alpha = 0.5,
        #            size = 0.5) +
        theme_apa()
